Models

### 2023-10-02 analysis/descriptive.qmd
more frustration

---
title: "Descriptive Analysis"
---

```{r setup, warning=FALSE, message=FALSE}

@@

# converting some columns to factors
factors <- c("sex", "race", "euro_mobility_90", "euro_mobility_180", "euro_mobility_365", "euro_selfcare_90", "euro_selfcare_180", "euro_selfcare_365", "euro_usual_90", "euro_usual_180", "euro_usual_365", "euro_pain_90", "euro_pain_180", "euro_pain_365", "euro_anxiety_90", "euro_anxiety_180", "euro_anxiety_365", "location_90", "location_180", "location_365", "ethnicity", "stroke", "cad", "chf", "afib", "pvd", "hld", "dm2", "tobacco", "htn_meds", "dm2_meds", "ich_location", "ich_laterality", "ivh", "evd", "neurosurgery_evac", "tracheostomy", "peg", "dnr_binary", "dni_binary", "comfort_care_binary", "mrs_90", "mrs_180", "mrs_365", "euroqol_90_assessment_source", "euroqol_180_assessment_source", "euroqol_365_assessment_source", "euro_mobility_365_binary", "euro_selfcare_365_binary", "euro_usual_365_binary", "euro_pain_365_binary", "euro_anxiety_365_binary", "study", "enrolling_country", "treatment_group", "euro_mobility_90_binary", "euro_selfcare_90_binary", "euro_usual_90_binary", "euro_pain_90_binary", "euro_anxiety_90_binary", "cocaine", "anticoagulated", "etoh", "mrs_270", "location_30")

data <- data |>
  mutate_at(factors, factor)

data <- data |>
  filter(ich_location == c("Lobar", "Basal Ganglia", "Thalamus")) |>
  filter(!is.na(ich_laterality))

```

```{r tableone}
#| fig-width: 20

@@

```

>>>>

#
#
#
#
#

@@

#
#
#
#
#
#| fig-width: 20

@@

#
#
#

### 2023-10-02 analysis/models.qmd
more frustration

library(tidyverse)
library(dagitty)
library(ggdag)
library(MetBrewer)
library(here)
library(brms)
library(broom)
library(tableone)

@@

@@

First let's do a Table 1

@@

CreateTableOne(data = data)

>>>>

library(tidyverse)
library(marginaleffects)
library(brms)
library(ggplot2)
library(ggdist)
library(broom)

@@

data <- data |>
  mutate(mrs_90 = fct_relevel(
    mrs_90,
    "0",
    "1",
    "2",
    "3",
    "4",
    "5",
    "6",
  ))

is.ordered(data$mrs_90)

@@

First let's do a replication of the INTERACT re-analysis.

@@

priors <- c(prior(normal(0, 1.5), class = Intercept))

inits <- list(Intercept = c(-2, -1, 0, 1, 2, 2.5))

mod <- brm(mrs_90 ~ 1,
  data = data,
  family = cumulative("logit"),
  prior = priors,
  init = rep(list(inits), 4),
  chains = 4, iter = 5000 * 2, seed = 28203, cores = 4,
  backend = "cmdstanr", refresh = 0
)
